From Binding Signatures to Bidirectional Typing

### 2022-09-19 tex/BiSig.tex
[ update ] Bidirectionally typed terms with type variables

The idea of including the presentation as well as the language itself appeared earlier~\cite{Hamana2011a,Fiore2013a,Arkor2020} and is essential for our development, since we need to recognise type variables in the binding signature for defining mode-correctness.

\paragraph{Language-formalisation frameworks} have been implemented in proof assistants and vary in design choices including the binding representation paradigm, the language presentation, how the formal syntax is instantiated, and more.
Due to the limited space we will only discuss frameworks that are somewhat of different characteristics.
Nevertheless, the interested reader is referred to the discussion by Gheri and Popescu~\cite[Section 8]{Gheri2020} for a more comprehensive list of frameworks.

>>>>

The idea of including the presentation of types as well as the language itself appeared earlier~\cite{Hamana2011a,Fiore2013a,Arkor2020} and is essential for our development, since we need to recognise type variables in the binding signature for defining mode-correctness.

\paragraph{Language-formalisation frameworks} have been implemented in proof assistants and vary in design choices including binding representation paradigms, language presentations, the instantiation of formal syntax, and more.
Due to the limited space the interested reader is referred to the discussion by Gheri and Popescu~\cite[Section 8]{Gheri2020} for a more comprehensive list of frameworks.
